\documentclass[12pt]{article}
\usepackage[letterpaper, margin=.75in]{geometry}

\title{PHI 227 - Assigned Notes}
\author{Lucas Vas}

\setlength{\parindent}{0pt}

\begin{document}

    \maketitle

    We should have read 3 articles on privacy - why are privacy/data intertwined with AI/Machine Learning?
    \begin{itemize}
        \item Data is collected, generally is a breach of privacy (someone gets the data without your consent)
        \item AI uses this data to "learn" - it's trained on this data
        \item Terms of service for aI are very broad, so they can use your data for whatever they want
        \begin{itemize}
            \item They're generally written in a way that's deliberately confusing
            \item Anything you write into these systems is kept in order to create an even larger data set
            \item Supposedly this process is anonymous, but who knows if that's true?
        \end{itemize}
        \item There's generally two large entities that want you data:
        \begin{itemize}
            \item The government
            \begin{itemize}
                \item (non-)state actors for their own personal interest (someone that's part of the government, but not the government itself)
            \end{itemize}
            \item The corporations
            \item Typically this comes down to how interesting of a person we are - do we have something that they want? Money? Power? Influence?
        \end{itemize}
        \item Storing data is exceptionally inexpensive, so there's no reason to delete it.
    \end{itemize}

    In the end, our data and the privacy that's a part of managing it is quite important. We should be aware of what we're giving up when we use these services.

    When we give up our data, we almost directly give away our own personal autonomy.

    \begin{itemize}
        \item We usually have the autonomy to choose what we do with our relationships.
        \item We interact differently with different groups of people.
        \item Should have control of our own personal information and space
        \begin{itemize}
            \item Giving out our data could breach this, and show \textit{everyone} what we do at any point in time.
        \end{itemize}
    \end{itemize}

    There are two main types of harms that can come from this:

    \begin{itemize}
        \item Individual harms - harms that affect the autonomy of the individual.
        \begin{itemize}
            \item Discrimination - perhaps you don't have a job because of your personal data, something such as a disability that gets in your way.
            \item Breach of personal information - someone gets your personal information and uses it against you.
            \begin{itemize}
                \item Identity Theft - company pretends to be you
                \item Eventual humiliation and/or social stigma
                \item Profiling (of any kind you can think of, not just racial)
            \end{itemize}
        \end{itemize}
        \item Collective harms - harms that affect the autonomy of a group of people.
        \begin{itemize}
            \item Total Surveillance - everyone is being watched all the time
            \item Chilling Effect on Free Speech - people are afraid to speak their mind
            \item Misinformation - people are fed false information, however now it's so easy to personalize it
        \end{itemize}
    \end{itemize}

    Corporations must take risks with our data because otherwise they don't make any money off of it. Is that really what we want to happen with our data?
    Doesn't seem like the greatest idea. \\

    There's also some issues with the way that we store our data. Since it's so inexpensive, corporations don't have any reason to delete it. This means that this
    data may eventually overflow out onto the internet, simply by virtue of it existing. This is a huge issue, and it's not really being addressed. \\

    Some have suggested a "data labor union" - corporations would have to negotiate a sum of money in order to access your data, then pay the union that amount. The
    union would then write a check out to you, the user, for the amount that was negotiated. This would give the user more control over their data, and would allow for
    some financial compensation for the use of their data. \\

\end{document}