\documentclass[12pt]{article}
\usepackage[letterpaper, margin=.75in]{geometry}
\usepackage{fancyhdr}

\title{Essay Outline}
\author{Lucas Vas}
\date{\today}

\begin{document}
    \maketitle

    \noindent\textbf{Thesis Statement:} The lack of explainability within AI models, with a focus on large language models that have been used to shape our
    decisions, raises serious ethical concerns due to the lack of fairness, accountability, and transparency, which leads to a lack of trust and holds back
    fully responsible deployment of AI into our everyday lives.

    \begin{itemize}
        \item[I.] \textbf{Introduction}
        \item[II.] \textbf{Violation of Transparency}
        \begin{itemize}
            \item[A.] Definition of transparency in the context of AI,
            \item[B.] Explanation of how transparency is important in everyday life.
            \item[C.] Touch upon AI's usage of our personal information?
        \end{itemize}
        \item[III.] \textbf{Violation of Accountability}
        \begin{itemize}
            \item[A.] Definition of accountability in the context of AI.
            \item[B.] Explanation of how AI's unexplainability hinders trust.
            \item[C.] Examples of scenarios where the lack of accountability has led to ethical challenges.
        \end{itemize}
        \item[IV.] \textbf{Violation of Fairness}
        \begin{itemize}
            \item[A.] Definition of fairness in the context of AI.
            \item[B.] Explanation of how inadequate explainability can lead to bias and discrimination.
            \item[C.] Real world examples of how AI systems have demonstrated biased outcomes.
        \end{itemize}
        \item[V.] \textbf{Conclusion}
    \end{itemize}
\end{document}